### 2020-06-04 2020/phd_midterm_report/report.tex
spelling error
correct pointed errors

\subsubsection*{Model-based adaptation methods}
These approaches take interest in the model architecture and model training process. We can further categorize them into 3 classes: feature-augmentation, module-augmentation, surrogate losses, and finetuning. In the class of feature-augmentation, \cite{Kobus17domain}, \cite{kenji17multi}, \cite{Pham19generic} proposed to add domain-tags and learn-able domain-embeddings to existing word feature of NMT model. These methods are cheap and efficient in terms of gain over model-size.

@@

\subsection*{Realized work}
The work of \cite{Kobus17domain} and \cite{Daume07frustratingly} showed promising results for learning in a multi-domain context. Inspired by the simplicity of the methods, we extend their works to a new version of domain embedding. In this method, each word has its domain embedding which amounts to a small share of the word embedding.

@@

\section*{Other research}
\subsection*{Semantic similarity}
\cite{pham18fixing} proposed a method to predict the semantic similarity between 2 sentences from 2 different languages. The method is used in the context of filtering noisy parallel corpora such as Paracrawl. The method was implemented for corpus filtering shared task  \cite{koehn18findings}. \cite{pham18fixing} used a siamese network to encode a bilingual pair of sentences whose embedding is used to compute the semantic similarity by cosine similarity. The training of the network is done by optimizing the aggregation of soft word alignment scores between 2 sentences. To avoid being over-fitted by positive examples in which every sentence pair is correctly matched, we proposed to use the same amount of artificial negative examples in which words are randomly removed or added and changed in several positions.
\section*{Provisional planning}
\begin{itemize}
	\item Completing work on residual adapters and submission to WMT 2020 at the end of July 2020.
	\item Completing system submission to Machine Translation Robustness task of WMT 2020 at the end of July 2020.
	\item Completing work on contextualized Machine Translation with Systran's team at the end of July 2020.
	\item Completing work on Multi-source Adaptation between August - December 2020
	\item Completing work on BPE-vocabulary's transfer learning effect between January and April 2021.
\end{itemize}
\bibliography{bibliography}
\bibliographystyle{apa-good}
\end{document}

>>>>

\subsubsection*{Model-based adaptation methods}
These approaches take interest in the model architecture and model training process. We can further categorize them into 3 classes: feature-augmentation, module-augmentation, surrogate losses, and finetuning. In the class of feature-augmentation, \cite{Kobus17domain}, \cite{kenji17multi}, \cite{Pham19generic} proposed to add domain-tags and learn-able domain-embeddings to existing word feature of NMT model. These methods achieve a good trade-off between performance gain and the number of additional parameters.

@@

\subsection*{Past contribution}
The work of \cite{Kobus17domain} and \cite{Daume07frustratingly} showed promising results for learning in a multi-domain context. Inspired by the simplicity of the methods, we extend their works to a new version of domain embedding. In this method, each word has its domain embedding which amounts to a small share of the word embedding.

@@

\section*{Other research}
\subsection*{Semantic similarity}
\cite{pham18fixing} proposed a method to predict the semantic similarity between 2 sentences from 2 different languages. The method is used in the context of filtering noisy parallel corpora such as Paracrawl. The method was implemented for corpus filtering shared task  \cite{koehn18findings}. \cite{pham18fixing} used a siamese network to encode a bilingual pair of sentences whose embedding is used to compute the semantic similarity by cosine similarity. The training of the network is done by optimizing the aggregation of soft word alignment scores between 2 sentences. To avoid being over-fitted by positive examples in which every sentence pair is correctly matched, we proposed to use the same amount of artificial negative examples in which words are randomly removed or added and changed in several positions.
\section*{Provisional planning}
\begin{itemize}
	\item Completing work on residual adapters and submission to WMT 2020 at the end of July 2020.
	\item Completing system submission to Machine Translation Robustness task of WMT 2020 at the end of July 2020.
	\item Completing work on contextualized Machine Translation with Systran's team at the end of July 2020.
	\item Completing work on Multi-source Adaptation between August - December 2020.
	\item Completing work on BPE-vocabulary's transfer learning effect between January and April 2021.
\end{itemize}
\bibliography{bibliography}
\bibliographystyle{apa-good}
\end{document}
